### 2024-06-23 Paper/MSEPM-Manuscript.tex
Update MSEPM-Manuscript.tex
retry to update file

Methylation sites were simulated by first randomly setting the dynamic range of the methylation site, 
$-1< \delta < 1$ a site intercept, $r^0_i$, and the site error, $\sigma_i \sim \mathcal{U}(0.025, 0.05)$. The dynamic 
range of the methylation site is described by the initial methylation value, $m_0 ~ \beta(.2,.2)$, 
and the target methylation value, $m_t$, where the dynamic range is $\delta_i = m_t - m_o$.
The value of $m_t$ is set conditionally to ensure dynamic range is always larger than some specified threshold, $\theta$, where 
$ \theta \leq|\delta| \geq. r^0_i ~ \beta(.2,.2)$.

Simulated methylation sites are then randomly associated with a combination of zero, one, or multiple epigenetic factors. Rates for sites 
associated with multiple factors were set by sampling from a uniform distribution. The weighted factor rates are normalized so 
the input combination of traits describes the dynamic range of the simulated site, $\delta$. If a site is associated 
with no factors the observed methylation status of a site is described by a random normal with a characteristic offset, $\hat{m_i} = r_{0,i} + N(\mu, \sigma)$.

@@

We simulated individuals whose methylation is determined by four factors and their associated epigenetic factors: 
a uniform factor approximating age with a non-linear association with methylation status 
$$q \sim\mathcal{U}(0,100), s_{Age}=q^{0.5}, \text{Figure 1A-B}$$ a binary trait resembling sex, linearly associated 
with methylation status $$q \sim B(1,.5), s_{Sex}=q, \text{Figure 1C-D}$$ a continuous normal (CN) phenotype a linear 
association with methylation status $$q \sim\mathcal{N}(1, 0.1), s_{CN}=q, 
\text{Figure 1E-F}$$ and a 
continuous exponentially (CE) distributed trait with a linear association with methylation status 
$$q \sim \frac{1}{20}e^{-x/20}, s_{CE}=q, \text{Figure 1G-H}$$

>>>>

Methylation sites were simulated by first randomly setting the range of the methylation site, 
$-1< \delta < 1$ a site intercept, $r^0_i$, and the site error, $\sigma_i \sim \mathcal{U}(0.025, 0.05)$. The possible 
range of the methylation site is described by the initial methylation value, $m_0 ~ \beta(.2,.2)$, 
and the target methylation value, $m_t$, where the range is $\delta_i = m_t - m_o$. $\beta(.2,.2)$ is the beta distribution with its parameters for randomly setting the sample.
The value of $m_t$ is set conditionally to ensure site variability is always larger than some specified threshold, $\theta$, where 
$ \theta \leq|\delta| \geq. r^0_i ~ \beta(.2,.2)$.

Simulated methylation sites are then randomly associated with a combination of zero, one, or multiple epigenetic factors. Rates for sites 
associated with multiple factors were set by sampling from a uniform distribution. The weighted factor rates are normalized so 
the input combination of traits describes the range of the simulated site, $\delta$. If a site is associated 
with no factors the observed methylation status of a site is described by a random normal with a characteristic offset, $\hat{m_i} = r_{0,i} + N(\mu, \sigma)$.

@@

We simulated individuals whose methylation is determined by four factors and their associated epigenetic factors: 
a uniformly distributed factor approximating age with a non-linear association with methylation status 
$$q \sim\mathcal{U}(0,100), s_{Age}=q^{0.5}, \text{Figure 1A-B}$$ a binary distributed trait resembling sex, linearly associated 
with methylation status $$q \sim B(1,.5), s_{Sex}=q, \text{Figure 1C-D}$$ a continuous normal (CN) phenotype a linear 
association with methylation status $$q \sim\mathcal{N}(1, 0.1), s_{CN}=q, 
\text{Figure 1E-F}$$ and a 
continuous exponentially (CE) distributed trait with a linear association with methylation status 
$$q \sim \frac{1}{20}e^{-x/20}, s_{CE}=q, \text{Figure 1G-H}$$
